### 2019-07-09 reports/thesis/chapters/4_variancePrediction.tex
printResults for GlmSelect

>>>>

\begin{sidewaystable}
\centering
\begin{tabular}{cc|ccc}
\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\
\\
\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}     
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
\centering
\begin{tabular}{cc|ccc}
\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\
\\
\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}     
\end{tabular}
\end{sidewaystable}
